Supplementary Materials

### 2021-01-20 analysis/analysis.Rmd
removing normality

## Index and Normality

Subgroup relations can be classified by their index, and by whether they are normal or not. Here we investigate the extent to which these two variables can account for the variation between the subgroup relationships.

@@

comp_summary$eeg %>% ungroup() %>%
   mutate(
     index = as.numeric(as.character(index)),
     normal = if_else(normal, 1, 0)) -> comp_summary$eeg

my_models$eeg <- brm(data = comp_summary$eeg, mean_value ~ index * normal)

@@

comp_summary$threshold %>% ungroup() %>%
   mutate(
     index = as.numeric(as.character(index)),
     normal = if_else(normal, 1, 0)) -> comp_summary$threshold

my_models$disp <- brm(data = comp_summary$threshold, mean_value ~ index * normal)

@@

It is unclear from the above summary tables whether either variable has a clear effect.

>>>>

## Index

Subgroup relations can be classified by their index. Here we investigate the extent to which index can account for the variation between the subgroup relationships.

@@

comp_summary$eeg %>% ungroup() %>%
   mutate(
     index = as.numeric(as.character(index))) -> comp_summary$eeg

my_models$eeg <- brm(
  data = comp_summary$eeg, 
  scale(mean_value) ~ index)

@@

comp_summary$threshold %>% ungroup() %>%
   mutate(
     index = as.numeric(as.character(index))) -> comp_summary$threshold

my_models$disp <- brm(
  data = comp_summary$threshold, 
  scale(mean_value) ~ index)

@@
